---
title: "RMarkdown-Homework-ODD_Analysis_Assignment2"
author: "Leyla Yigit"
date: "31 Ekim 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the package to the session
library(tidyverse)
library(readxl)
library(plyr)
#install.packages("magrittr") library(magrittr)
#dd <- "plyr"
#install.packages(dd)

```




```{r cars}
#Download Raw Data
# Create a temporary file
tmp<-tempfile(fileext=".xlsx")
# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/pj18-Leyla.Yigit/blob/master/FILES/odd_retail_sales_2016_10.xlsx?raw=true",mode="wb",destfile=tmp)
# Read that excel file using readxl package's read_excel function. You might need to adjust the parameters (skip, col_names) according to your raw file's format.
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
# Remove the temp file
file.remove(tmp)
```

## Remove the last two rows because they are irrelevant (total and empty rows)


```{r pressure}
plot(pressure)
raw_data <- raw_data %>% slice(-c(48,49))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Let's see our raw data

```{r pressure}
head(raw_data)
```


## Make Data Civilized

```{r pressure}
#In order to make the data standardized and workable we need to define column names and remove NA values for this example. 
#Please use the same column names in your examples also.
# Use the same column names in your data.
colnames(raw_data) <- c("MARKA","oto_yerli","oto_ithal","oto_toplam","ticari_yerli","ticari_ithal","ticari_toplam","toplam_yerli","toplam_ithal","toplam_toplam")
# Now we replace NA values with 0 and label the time period with year and month, so when we merge the data we won't be confused.
car_data_oct_16<- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>% mutate(year=2016,month=10)

print(car_data_oct_16,width=Inf)
```


## Save Your Civilized Data

```{r pressure}
#One of the best methods is to save your data to an RDS or RData file. 
#The difference is RDS can hold only one object but RData can hold many. Since we have only one data frame here we will go with RDS.
# Save an object to a file
saveRDS(car_data_oct_16, file = "car_data_oct_16.rds")
```


##ANALYSIS
## --1--- a list of total sales of brands with both automobile and commercial vehicle sales ordered in decreasing total sales.

```{r pressure}
car_data_oct_16 %>% 
  filter(oto_toplam > 0 & ticari_toplam > 0) %>%
  select(MARKA,toplam_toplam) %>%
  arrange(desc(toplam_toplam))
```

## Analysis Result:VOLKSWAGEN has the highest number of sales; on the other hand SSANGYONG has the lowest sales number: 























